Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
make abstract and vision more consistent

\begin{abstract}
  \Hydras is a collaborative library of discrete mathematics for the
  \coq proof assistant, developed as part of the \community project
  on GitHub. The Coq code is accompanied
  by an electronic book, generated with the help of the \alectr
  literate proving tool. We present the evolution of the mathematical
  contents of the library since former presentations at JFLA meetings.
  Then, we describe how the structure of the project is determined
  by two requirements which must be continuously satisfied.
  First, the Coq code needs to be compatible with its ever-evolving
  dependencies (the Coq proof assistant and several Coq packages both from
  inside and outside \community) and reverse dependencies (\community
  projects that depend on it). Second, the book needs to be consistent
  with the Coq code, which undergoes frequent changes to improve
  structure and include new material. We believe \Hydras demonstrates
  that books on formalized mathematics are not limited to
  providing exposition of theories and reasoning techniques---they
  can also provide inspiration and entertainment that transcends educational goals.
\end{abstract}

@@

Libraries of formalized mathematics based on proof assistants, such as \coq, Lean, and Isabelle/HOL, are continually growing in size and scope.
For example, the core projects in the Mathematical Components family for Coq amount to more than 160,000 lines of code and 11,000 lemmas~\cite{Nie2020a}, while Lean's Mathlib consists of more than 140,000 lines of code and 34,000 declarations~\cite{Mathlib}. However, after a key mathematical definition or result is added to a library, it needs be \emph{documented} and \emph{maintained}~\cite{vanDoorn2020}.

@@

\subsection{Vision}
The \Hydras project, part of \community~\cite{CoqCommunity}, aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \community is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting \coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting \coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor and Additions libraries (under the new names of Hydra-battles and Addition-chains), the Ackermann sub-library, extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel} and a bridge to the \gaia library (by José Grimm~\cite{Gaia,grimm:hal-00911710}).
%
By following this approach of commenting interesting \coq packages, we provide new documentation content, that contributes to the diversity of the thriving \coq documentation ecosystem.

>>>>

\begin{abstract}
  \Hydras is a collaborative library of discrete mathematics for the
  \coq proof assistant, developed as part of the \community organization
  on GitHub. The Coq code is accompanied
  by an electronic book, generated with the help of the \alectr
  literate proving tool. We present the evolution of the mathematical
  contents of the library since former presentations at JFLA meetings.
  Then, we describe how the structure of the project is determined
  by two requirements which must be continuously satisfied.
  First, the Coq code needs to be compatible with its ever-evolving
  dependencies (the Coq proof assistant and several Coq packages both from
  inside and outside \community) and reverse dependencies (\community
  projects that depend on it). Second, the book needs to be consistent
  with the Coq code, which undergoes frequent changes to improve
  structure and include new material. We believe \Hydras demonstrates
  that books on formalized mathematics are not limited to
  providing exposition of theories and reasoning techniques---they
  can also provide inspiration and entertainment that transcends educational goals.
\end{abstract}

@@

Libraries of formalized mathematics based on proof assistants, such as \coq, Lean, and Isabelle/HOL, are continually growing in size and scope.
For example, the core projects in the Mathematical Components family for Coq amount to more than 160,000 lines of code and 11,000 lemmas~\cite{Nie2020a}, while Lean's Mathlib consists of more than 140,000 lines of code and 34,000 declarations~\cite{Mathlib}. However, after a key mathematical definition or result is added to a library, it needs be \emph{documented}~\cite{alectryonpaper} and \emph{maintained}~\cite{vanDoorn2020}.

@@

\subsection{Vision}
The \Hydras project, part of \community on GitHub~\cite{CoqCommunity}, aims to be an experimental platform for the collaborative development of documented libraries of formal proofs. \community is a community organization that we founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting \coq packages, and working collaboratively on documentation projects. The \Hydras project demonstrates that these two goals are not independent: interesting \coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor~\cite{CantorContrib} and Additions~\cite{AdditionsContrib} libraries (under the new names of Hydra-battles and Addition-chains), the Ackermann sub-library which was extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel}, and a bridge to the \gaia library by José Grimm~\cite{Gaia,grimm:hal-00911710}.
%
By following this approach of commenting interesting \coq packages, we provide new documentation content that contributes to the diversity of the thriving \coq documentation ecosystem.
